### 2023-04-03 main.tex
k

\noindent
\textbf{Remara}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
By the Lie algebra above we describe the process with generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements

@@

\textbf{Remara}:

@@

\textbf{Remara}: in the reversible situation, i.e. when $\forall x\in V$ $\alpha_{a}^{x}=\alpha_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, p_{1},\ldots,p_{N}\right)$ is

@@

    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|

@@

%We now search for a symmetry of $H_{x,y}$. % Given $A,B\in gl(N)$, we say that $A$ is a symmetry of $B$ if 
%\begin{equation}
%    [A,B]=0
%\end{equation}
Since the coproduct is a Lie algebra homomorphism we have that $\forall A,B\in gl(N)$
\begin{equation}\label{symmetryCoproduct}
    [A,B]=0\quad \Longrightarrow\quad \left[\Delta(A),\Delta(B)\right]=0
\end{equation}
%Since $H_{x,y}$ is a linear function of the coproduct of the second Casimir, as a consequence of \eqref{symmetryCoproduct}, it is enough to identify a symmetry of $C_{2}$. But
 $C_{2}$ is in the center of $gl(N)$, and therefore it commutes with all the element of the the algebra. Considering 
\begin{equation}\label{equationE}
    E=\sum_{a=2}^{N}E_{a1}
\end{equation}
to obtain a product structure of the elements \eqref{dualityElements} of the duality matrix, we chose as a symmetry 
\begin{equation}
    S=\exp{(\Delta(E))}
\end{equation}
%Since $[C_{2},E]=0$, we have that 
%\begin{equation}\label{commutationSC}
    %\left[S,\Delta(C_{2})\right]=0
%\end{equation}
For fixed $(x,y)\in \mathcal{E}$ we introduce
\begin{equation}
    S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
\end{equation}
where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence of \eqref{symmetryCoproduct}, we have that 
\begin{equation}\label{symmetryH}
    \left[S_{x,y},H_{x,y}\right]=0
\end{equation}
i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Finally, we obtain that 
\begin{equation}
    \begin{split}
        H_{x,y}^{T}D&=(R_{x}R_{y})H_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\widehat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\widehat{y}}\right)H_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        \\&=
        DH_{x,y}
    \end{split}
\end{equation}
 where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
 %\textbf{Remara}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{a}$ is lower or equal than the number of original particles $n_{a}^{x}$. This implies that the dynamics of the dual process is simpler, because described by a lower number of particles. By the way, it is possible to perform computations similar to the one made in this proof choosing instead of  \eqref{equationE} {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
 %{\color{blue} That's confusing. What is E?}

@@

	H=B_{1}+H_{bula}+B_{L}

@@

    H_{bula}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}

@@

\textbf{Remara}: only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}

@@

   H=\left(\mathcal{V}^{-1}\right)^{T}\widehat{H}^{T}V^{T}

@@

    \mathbb{H}=\mathbb{B}_{1}+H_{bula}+\mathbb{B}_{L}

@@

\subsubsection{The steady state of $\widehat{H}$}

@@

\textbf{Remara}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $s_{x}\neq 1$ $\forall i\in \{1,\ldots,L\}$, then the second addend vanishes and, for these particular configurations, 

@@

We rewrite
\begin{equation}
	\begin{split}
	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
	\end{split}
\end{equation}
\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)\\
	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{a=2}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{a=2}^{N}e_{ja}^{[a]}e_{a1}^{[b]}}
\end{split}
\end{equation}
\textbf{Remara}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

@@

\textbf{Remara}: The basis element the we have defined above, can also be thought as proper compositions of the rising and lowering operators of th Heisenberg Lie algebra. Indeed, \begin{equation}\label{creationOperators}

@@

The algebra $gl(N)$ is isomorphic to $su(N)$ and we have chosen a $2j$ spin representation of it. It is also possible to see that this representation can be written as a direct sum of representation of $su(2)$, each with representation $2j$ and each associated with a positive root. The generator of this $su(2)$ sub-algebras can be written by:  $J^{+}=e_{ab}$, $J^{-}=e_{ba}$, $J^{0}=1/2(e_{bb}-e_{aa})$ $\forall a,b=1,\ldots,N$. \\
The explicit actions of the basis element of the algebra on the vectors of the space $\mathcal{C}^{D}$ are the following, for non Cartan and Cartan elements respectively: 
\begin{equation}
	\begin{cases}
		e_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\\
		e_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle
	\end{cases}\qquad \forall a,b\in\{1,\ldots,N\}
\end{equation}
In matrix form $\forall a,b\in \{1,\ldots,N\}$
\begin{equation}\label{matrixFormulaE}
	\begin{split}
	&e_{ab}=\sum_{n\in\chi}n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots n_{N}\rangle \langle n_{1},\ldots,n_{N}|
	\end{split}
\end{equation}
\textbf{Remara}: in this algebraic setting it is more convenient to use the \textit{Bra-Ket} notation for the states of the process. The mapping with the vectors written in \eqref{stateSpace} is the following
\begin{equation}
(n_{1}^{x},\ldots,n_{N}^{x})^{T}=|n_{1},\ldots,n_{N}\rangle_{x}\qquad(n_{1}^{x},\ldots,n_{N}^{x})=\langle n_{1},\ldots,n_{N}|_{x}
\end{equation}
\begin{flushright}
    $\square$
\end{flushright}
This Lie algebra has second Casimir element given by 
\begin{equation}
    C_{2}=\sum_{a,b=1}^{N}e_{ab}e_{ba}
\end{equation}
This element is diagonal, and its action on a generic state is the following:
\begin{equation}
	C_{2}=2j(2j+N)\mathbbm{1}
\end{equation}
where $\mathbbm{1}$ is the $D\times D$ dimensional identity matrix. \\
By introducing the \textit{coproduct} operator \begin{equation}\begin{split}\Delta:(\mathbb{C}^{D},\Pi)&\to(\mathbb{C}^{D}\otimes \mathbb{C}^{D},\Pi\otimes \Pi) \\
 e_{ab}&\to e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}
\end{split}
\end{equation}
then we can compute 
\begin{equation}\label{coproductC2}
	\begin{split}
	\Delta(C_{2}&)=\sum_{a,b=0}^{N}\Delta(e_{ab})\Delta(e_{ba})
	=
	\sum_{a,b=0}^{N}\left(\mathbbm{1}\otimes e_{ab}+e_{ab}\otimes \mathbbm{1}\right)\left(\mathbbm{1}\otimes e_{ba}+e_{ba}\otimes \mathbbm{1}\right)
	\\&=
	\sum_{a,b=0}^{N}\left(\mathbbm{1}\otimes e_{ab}e_{ba}+e_{ba}\otimes e_{ab}+e_{ab}\otimes e_{ba}+e_{ab}e_{ba}\otimes \mathbbm{1}\right)
	\\&=
	2\left(\sum_{a,b=0}^{N}e_{ab}\otimes e_{ba}\right)+\mathbbm{1}\otimes C_{2}+C_{2}\otimes\mathbbm{1}
	\end{split}
\end{equation}
We now define the equivalent of \eqref{stateSpace} in the vector notation
 \begin{equation}
	\Omega:=\left\{|n_{1},\ldots,n_{N}\rangle \;:\;\sum_{a=1}^{N}n_{a}=2j\right\}^{\otimes|V|}
	\end{equation}
where we denote 
\begin{equation}
|n\rangle=\bigotimes_{x\in V}	\left(|n_{1},\ldots,n_{N}\rangle_{x}\right)\in \Omega
\end{equation}
The Hamiltonian operator can be written in term of the basis element of the Lie algebra as

>>>>

\noindent
\textbf{Reamrk}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
By the Lie algebra above we describe the process with generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements

@@

\textbf{Reamrk}:

@@

\textbf{Reamrk}: in the reversible situation, i.e. when $\forall x\in V$ $\alpha_{a}^{x}=\alpha_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, p_{1},\ldots,p_{N}\right)$ is

@@

    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}!}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|

@@

%We now search for a symmetry of $H_{x,y}$. % Given $A,B\in gl(N)$, we say that $A$ is a symmetry of $B$ if 
%\begin{equation}
%    [A,B]=0
%\end{equation}
Since the coproduct is a Lie algebra homomorphism we have that $\forall A,B\in gl(N)$
\begin{equation}\label{symmetryCoproduct}
    [A,B]=0\quad \Longrightarrow\quad \left[\Delta(A),\Delta(B)\right]=0
\end{equation}
%Since $H_{x,y}$ is a linear function of the coproduct of the second Casimir, as a consequence of \eqref{symmetryCoproduct}, it is enough to identify a symmetry of $C_{2}$. But
 $C_{2}$ is in the center of $gl(N)$, and therefore it commutes with all the element of the the algebra. Considering 
\begin{equation}\label{equationE}
    E=\sum_{a=2}^{N}E_{a1}
\end{equation}
to obtain a product structure of the elements \eqref{dualityElements} of the duality matrix, we chose as a symmetry 
\begin{equation}
    S=\exp{(\Delta(E))}
\end{equation}
%Since $[C_{2},E]=0$, we have that 
%\begin{equation}\label{commutationSC}
    %\left[S,\Delta(C_{2})\right]=0
%\end{equation}
For fixed $(x,y)\in \mathcal{E}$ we introduce
\begin{equation}
    S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
\end{equation}
where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence of \eqref{symmetryCoproduct}, we have that 
\begin{equation}\label{symmetryH}
    \left[S_{x,y},H_{x,y}\right]=0
\end{equation}
i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Finally, we obtain that 
\begin{equation}
    \begin{split}
        H_{x,y}^{T}D&=(R_{x}R_{y})H_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\widehat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\widehat{y}}\right)H_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        \\&=
        DH_{x,y}
    \end{split}
\end{equation}
 where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
 %\textbf{Reamrk}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{a}$ is lower or equal than the number of original particles $n_{a}^{x}$. This implies that the dynamics of the dual process is simpler, because described by a lower number of particles. By the way, it is possible to perform computations similar to the one made in this proof choosing instead of  \eqref{equationE} {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
 %{\color{blue} That's confusing. What is E?}

@@

	H=B_{1}+H_{bulk}+B_{L}

@@

    H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}

@@

\textbf{Reamrk}: only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}

@@

   H=\left(\mathcal{V}^{-1}\right)^{T}\widehat{H}^{T}\mathcal{V}^{T}

@@

    \mathbb{H}=\mathbb{B}_{1}+H_{bulk}+\mathbb{B}_{L}

@@

\subsubsection{The steady state of $\widehat{H}^{T}$}

@@

\textbf{Reamrk}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $s_{x}\neq 1$ $\forall i\in \{1,\ldots,L\}$, then the second addend vanishes and, for these particular configurations, 

@@

We rewrite
\begin{equation}
	\begin{split}
	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
	\end{split}
\end{equation}
\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)\\
	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{a=2}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{a=2}^{N}e_{ja}^{[a]}e_{a1}^{[b]}}
\end{split}
\end{equation}
\textbf{Reamrk}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

@@

\textbf{Reamrk}: The basis element the we have defined above, can also be thought as proper compositions of the rising and lowering operators of th Heisenberg Lie algebra. Indeed, \begin{equation}\label{creationOperators}

@@

The algebra $gl(N)$ is isomorphic to $su(N)$ and we have chosen a $2j$ spin representation of it. It is also possible to see that this representation can be written as a direct sum of representation of $su(2)$, each with representation $2j$ and each associated with a positive root. The generator of this $su(2)$ sub-algebras can be written by:  $J^{+}=e_{ab}$, $J^{-}=e_{ba}$, $J^{0}=1/2(e_{bb}-e_{aa})$ $\forall a,b=1,\ldots,N$. \\
The explicit actions of the basis element of the algebra on the vectors of the space $\mathcal{C}^{D}$ are the following, for non Cartan and Cartan elements respectively: 
\begin{equation}
	\begin{cases}
		e_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\\
		e_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle
	\end{cases}\qquad \forall a,b\in\{1,\ldots,N\}
\end{equation}
In matrix form $\forall a,b\in \{1,\ldots,N\}$
\begin{equation}\label{matrixFormulaE}
	\begin{split}
	&e_{ab}=\sum_{n\in\chi}n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots n_{N}\rangle \langle n_{1},\ldots,n_{N}|
	\end{split}
\end{equation}
\textbf{Reamrk}: in this algebraic setting it is more convenient to use the \textit{Bra-Ket} notation for the states of the process. The mapping with the vectors written in \eqref{stateSpace} is the following
\begin{equation}
(n_{1}^{x},\ldots,n_{N}^{x})^{T}=|n_{1},\ldots,n_{N}\rangle_{x}\qquad(n_{1}^{x},\ldots,n_{N}^{x})=\langle n_{1},\ldots,n_{N}|_{x}
\end{equation}
\begin{flushright}
    $\square$
\end{flushright}
This Lie algebra has second Casimir element given by 
\begin{equation}
    C_{2}=\sum_{a,b=1}^{N}e_{ab}e_{ba}
\end{equation}
This element is diagonal, and its action on a generic state is the following:
\begin{equation}
	C_{2}=2j(2j+N)\mathbbm{1}
\end{equation}
where $\mathbbm{1}$ is the $D\times D$ dimensional identity matrix. \\
By introducing the \textit{coproduct} operator \begin{equation}\begin{split}\Delta:(\mathbb{C}^{D},\Pi)&\to(\mathbb{C}^{D}\otimes \mathbb{C}^{D},\Pi\otimes \Pi) \\
 e_{ab}&\to e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}
\end{split}
\end{equation}
then we can compute 
\begin{equation}\label{coproductC2}
	\begin{split}
	\Delta(C_{2}&)=\sum_{a,b=0}^{N}\Delta(e_{ab})\Delta(e_{ba})
	=
	\sum_{a,b=0}^{N}\left(\mathbbm{1}\otimes e_{ab}+e_{ab}\otimes \mathbbm{1}\right)\left(\mathbbm{1}\otimes e_{ba}+e_{ba}\otimes \mathbbm{1}\right)
	\\&=
	\sum_{a,b=0}^{N}\left(\mathbbm{1}\otimes e_{ab}e_{ba}+e_{ba}\otimes e_{ab}+e_{ab}\otimes e_{ba}+e_{ab}e_{ba}\otimes \mathbbm{1}\right)
	\\&=
	2\left(\sum_{a,b=0}^{N}e_{ab}\otimes e_{ba}\right)+\mathbbm{1}\otimes C_{2}+C_{2}\otimes\mathbbm{1}
	\end{split}
\end{equation}
We now define the equivalent of \eqref{stateSpace} in the vector notation
 \begin{equation}
	\Omega:=\left\{|n_{1},\ldots,n_{N}\rangle \;:\;\sum_{a=1}^{N}n_{a}=2j\right\}^{\otimes|V|}
	\end{equation}
where we denote 
\begin{equation}
|n\rangle=\bigotimes_{x\in V}	\left(|n_{1},\ldots,n_{N}\rangle_{x}\right)\in \Omega
\end{equation}
The Hamiltonian operator can be written in term of the basis element of the Lie algebra as
